Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-13 aistats.tex
Add self-concordance sample complexity

\subsection{Locally Quadratic Case}
FromTaylor expansion~~\eqref{eq:bregmanTaylor}, 
we know that all Bregman divergences are locally quadratic.
Under some assumptions, like self-concordance of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21 
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2
}
\end{proposition}
Proof in the appendix
\footnote{In case the reader is intrigued, $0.21$ is a value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}.
We know that $\conj$ is self-concordant when $T$ is 1-dimensional and $\logpart$ is self-concordant.
This is true for
exponential distributions,
Gaussians with known mean,
Laplace with known mean,
Pareto with known minimum value,
or Weibull with known shape $k$. 
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic}.

>>>>

\subsection{Locally Quadratic Case}
FromTaylor expansion~~\eqref{eq:bregmanTaylor}, 
we know that all Bregman divergences are locally quadratic.
Under some assumptions, like self-concordance of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21 
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2
}
\end{proposition}
Proof in the appendix
\footnote{In case the reader is intrigued, $0.21$ is a value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}.
To gain insights into how many samples are needed, we can estimate when $\expecti{\norm{\m^*-\m}_{\mF}} < 0.21 $.
For the MLE, $\expecti{\norm{\m^*-\hat \m_n}_{\mF}} = \frac{d}{n}$, so a sufficient condition is $n \geq 5 d$.
For MAP, using~\eqref{eq:MAP_quadratic}, we get the sufficient condition $n\geq 5d + \sqrt{5}\norm{\m^* -  \m_0} - n_0$ (see appendix).
This means that on average, we need much more samples than the dimension to reach the quadratic regime.

We know that $\conj$ is self-concordant when $T$ is 1-dimensional and $\logpart$ is self-concordant.
This is true for
exponential distributions,
Gaussians with known mean,
Laplace with known mean,
Pareto with known minimum value,
or Weibull with known shape $k$. 
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic}.
